### 2019-03-16 papers/journal/model.tex
Minor update on dia
cleaning of comment
added the number of mole and dependency text

\ashu{Should be written bio people}
Let us discuss rough sizes of the system and expected behaviors.
%
A typical VTS may have about 10 compartments.
%
%Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
%contain higher numbers (humans have 41)~\cite{kloepper2007elaborate}..
%
The VTS may transport a large number of molecules but the molecules that
are relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
%
According to the definition the activity of molecules can be controlled by
the presence of all other molecules.
%
However, in practice the activity of a molecule is controlled by
the presence of ~2-3 other molecules.

>>>>

Let us discuss rough sizes of the system and expected behaviors.
%%
%A typical VTS may have about 10 compartments.
%%
%%Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
%%contain higher numbers (humans have 41)~\cite{kloepper2007elaborate}..
%%
%The VTS may transport a large number of molecules but the molecules that
%are relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
%%
%According to the definition the activity of molecules can be controlled by
%the presence of all other molecules.
%%
%However, in practice the activity of a molecule is controlled by
%the presence of ~2-3 other molecules.
A typical eukaryotic cell contains 9 organelles; the ER, the cis-, medial- and trans-Golgi, the early, late and recycling endosomes, the lysosome and the plasma membrane~\cite{lodish2008molecular}. 
%
The organellar content of cells vary across different organisms, for example, parasitic cells such as Trypanosomes have specialized secretory organelles called rhopteries and micronemes~\cite{gubbels2012evolution}. 
%
The organellar content may also vary across different states of the same cell, for e.g., during cell division, the Golgi apparatus disintegrates into vesicles~\cite{tang2013cell}. 
%
Also, across different cell-types, these organelles may be more or less differentiated, for example, number of stacks in the Golgi vary across different cells~\cite{polishchuk2004structural}. 
%
Going by the above description, we can assume that the VTS has of the order of 10 compartments. 
%
The VTS transports a large number of molecules but the molecules that actively control the system are in their tens [MBOC]. 
%
By definition the activity of any VTS molecules can be controlled by all other molecules.
%
However, in practice the activity of a molecule is directly controlled by 2-3 other molecules; for example, adaptor proteins are recruited to compartments by lipids of the compartment membrane and by ARF/SAR GTPases~\cite{kahn2009toward}. 
%
Some molecules, such as Rab GTPases are master regulators which control many different VTS molecules with diverse functions~\cite{zerial2001rab}. 
%
But most VTS molecules have more localized influence.
